Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-06-15 Scripts/Initial_Analysis.Rmd
Changes in climate function

          F_BData <- Data[1]

@@

          F_BData <- cbind(Data[1],F_BData)
        }
}

@@

F_BData <- F_BData %>% 
          rowid_to_column("index") %>% 
  gather("year","temp",-index) %>% 
  write_csv(.,
            "SST_data.csv")

>>>>

          F_BData <- Data[1]
          colnames(F_BData) <- 2020

@@

          F_BData <- cbind(Data[1],F_BData)
          colnames(F_BData)[y] <- Years[y]
        }
}

@@

F_BData <- F_BData %>% 
          rowid_to_column("index") %>% 
  %>% 
  mutate(temp = ifelse(temp == -9999,NA,temp)) %>% 
  group_by(year) %>% 
  summarise(
    mean_temp = mean(temp,na.rm=T)
  ) %>% 
  gather("year","temp",-index) %>% 
  write_csv(.,
            "SST_data.csv")

```{r temp_plot, eval = T, echo = T}

sst_data <- my_path("D",T,"Climate","SST_data.csv",read = T)

ggplot(sst_data) +
  geom_line(
    aes(
      x = year,
      y = mean_temp
    )
  )
